---
title: "Data from twitter into table"
author: "Sara"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  rmdformats::downcute
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goals

- get some data from twitter via the twitter API, to get familiar with retrieving data via API
- put together a decent-looking table and get familiar with some another table formatting package

```{r, warning=FALSE, message=FALSE}
require(httr)
require(jsonlite)
require(dplyr)
require(htmltools)
require(reactable)
library(htmlwidgets)
```

# set up access

Before being able to run this, I have to set up a twitter developer account to get an access token. After setting this up, I can run this in the console `Sys.setenv(BEARER_TOKEN = "your-bearer-token")`

then access the token like this:

```{r}
bearer_token <- Sys.getenv("BEARER_TOKEN")
headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))
```

# Different functions for getting data

## get characteristics of a user account
```{r}
get_characteristics <- function(handle, headers){
  url_handle <-
  sprintf('https://api.twitter.com/2/users/by?usernames=%s&user.fields=created_at,description,id,name,profile_image_url,public_metrics', handle)
response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers))
obj <- httr::content(response, as = "text")
json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
}
```

```{r, warning=FALSE}
# test it
my_chars <- get_characteristics("SaraHaenzi", headers)
```

## get recent tweets
the standard developer account does not allow to retrieve all tweets, but only the most recent ones (last 7 days)

```{r}
get_recent_tweets <- function(handle, headers){
  params = list(
  `query` = sprintf('from:%s', handle)
)
  response <-
  httr::GET(url = "https://api.twitter.com/2/tweets/search/recent",
            httr::add_headers(.headers = headers),
            query = params)
  obj <- httr::content(response, as = "text")
json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
}

```

test it 
```{r}
my_recent <- get_recent_tweets("SaraHaenzi", headers)
```

## get number of likes
```{r}
get_n_likes <- function(ids_list, headers){
  ids_one_string <- paste(ids_list, collapse = ",")
  url_handle <- sprintf("https://api.twitter.com/2/tweets?ids=%s&tweet.fields=public_metrics", ids_one_string)
  response <-
  httr::GET(url_handle,
            httr::add_headers(.headers = headers))
  obj <- httr::content(response, as = "text")
  json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
  likes <- sum(json_data$data.public_metrics.like_count)
}
```

test it
```{r}
my_likes <- get_n_likes(my_recent$data.id, headers)
```

## get retweets
```{r}
get_n_retweets <- function(id, headers){
  url_handle <- sprintf("https://api.twitter.com/1.1/statuses/retweeters/:%s.json", id)
  response <- 
    httr::GET(url_handle,
            httr::add_headers(.headers = headers))
  obj <- httr::content(response, as = "text")
  json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame
}
```

test it
```{r}
retweets <- get_n_retweets(my_recent$data.id[[1]], headers)
```
with my current account I do not have access to this endpoint :-/ therefore cannot include retweets

## further data munging functions

```{r}
clean_column_names <- function(user_characteristics){
  user_characteristics %>%
  rename_all(~stringr::str_replace(.,"^data.","")) %>% # remove data. at the beginning of column names
  rename_all(~stringr::str_replace(., "^public_metrics.", "")) %>% # remove public_metrics.
  mutate(since = strtoi(stringr::str_sub(created_at, 1,4)))
}
```

```{r}
summarise_tweets <- function(tweets){
  tweets %>%
  tidyr::unnest(cols = c(likes)) %>%
  group_by(handles) %>%
  summarise(recent_tweets = n(),
            recent_likes = sum(likes))
}
```

```{r}
download_profile_pics <- function(user_characteristics){
  for (i in (1:nrow(user_characteristics))) {
  url <- user_characteristics$profile_image_url[[i]]
  name <- user_characteristics$handles[[i]]
  download.file(url ,destfile=sprintf("images/%s.jpg", name))
}
}
```

## bar chart function for table

```{r}
# Render a bar chart with a label on the left
bar_chart <- function(label, width = "100%", height = "14px", fill = "#00bfc4", background = NULL) {
  bar <- div(style = list(background = fill, width = width, height = height))
  chart <- div(style = list(flexGrow = 1, marginLeft = "6px", background = background), bar)
  div(style = list(display = "flex", alignItems = "center"), label, chart)
}
```

# Retrieve data from twitter round 1: different data visualisation accounts

```{r}
handles <- c("SWRdata", "BR_data", "SPIEGEL_Data", "SRFdata", "NZZvisuals")
country <- c("DE", "DE", "DE", "CH", "CH")
user_characteristics <- tibble(handles, country) %>%
  mutate(data_user = purrr::map(.x=handles, .f=get_characteristics, headers=headers)) %>%
  tidyr::unnest(cols = c(data_user))
tweets <- tibble(handles) %>%
  mutate(data_recent_tweets = purrr::map(.x=handles, .f=get_recent_tweets, headers=headers)) %>%
  tidyr::unnest(cols = c(data_recent_tweets)) %>%
  mutate(likes = purrr::map(.x=data.id, .f=get_n_likes, headers = headers))
```

```{r}
# rename columns
user_characteristics <- clean_column_names(user_characteristics) 

# summarise tweets
tweet_summary <- summarise_tweets(tweets)
```

select a subset of the user characteristics and join with the tweet summary
```{r}
subset <- user_characteristics %>%
  select(name = handles, country, since, followers = followers_count, tweets = tweet_count) %>%
  full_join(tweet_summary, by = c(name = "handles"))
```

download all the profile pictures
```{r}
download_profile_pics(user_characteristics)
```

this kind of works but the picture is tiny and the quality is awful. will do this manually... and save as png

# format the table nicely

very helpful [demo page for reactable](https://glin.github.io/reactable/articles/cookbook/cookbook.html)

duplicate name column for image
```{r}
subset <- subset %>%
  mutate(image_twitter = name) %>%
  relocate(image_twitter, .before = name)
```

make table
```{r}
my_font <- "corbel"
r <- reactable(subset,
          defaultSorted = "since", defaultSortOrder = "desc",
          rowStyle = function(index) {
            if (subset[index, "name"] == "SWRdata") list(background = "rgba(0, 0, 0, 0.05)")},
          columns = list(
            image_twitter = colDef(name = "", 
                          width = 60,
                          cell = function(value) {
                               img_src <- knitr::image_uri(sprintf("images/%s.png", value)) # .png for the manual download, .jpg for automatic
                               image <- img(src = img_src, height = "28px", alt = "")
                               tagList(
                                 div(style = list(display = "inline-block", width = "45px"), image),
                                 )
                               }),
            name = colDef(name = "Twitter-Konto", 
                          format = colFormat(prefix = "@"),
                          width = 150,
                          style = list(fontFamily = my_font)),
            country = colDef(name = "Land",
                             cell = function(value) {
                               img_src <- knitr::image_uri(sprintf("images/%s.png", value))
                               image <- img(src = img_src, height = "20px", alt = "")
                               tagList(
                                 div(style = list(display = "inline-block", width = "40px"), image),
                                 )
                               },
                             width = 60,
                             align = "center",
                             ),
            since = colDef(name = "dabei seit",
                           align = "center",
                           style = list(fontFamily = my_font)),
            followers = colDef(name = "Follower",
                               cell = function(value){
                                 width <- paste0(value*100 / max(subset$followers), "%")
                                 value <- format(value, width = 7, justify = "right")
                                 bar_chart(value, width=width, fill = "#06B4E6", background = "#e1e1e1")
                               },
                               align = "left",
                               width = 180,
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            tweets = colDef(name = "Tweets total",
                            cell = function(value){
                                 width <- paste0(value*100 / max(subset$tweets), "%")
                                 value <- format(value, width = 5, justify = "right")
                                 bar_chart(value, width=width, fill = "#4D65AC", background = "#e1e1e1")
                               },
                               align = "left",
                              width = 180,
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            recent_tweets = colDef(name = "Tweets letzte Woche",
                                   cell = function(value){
                                 width <- paste0(value*100 / max(subset$recent_tweets), "%")
                                 value <- format(value, width = 2, justify = "right")
                                 bar_chart(value, width=width, fill = "#644796", background = "#e1e1e1")
                               },
                               align = "left",
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            recent_likes = colDef(name = "Likes letzte Woche",
                                  cell = function(value){
                                 width <- paste0(value*100 / max(subset$recent_likes), "%")
                                 value <- format(value, width = 2, justify = "right")
                                 bar_chart(value, width=width, fill = "#4C2360", background = "#e1e1e1")
                               },
                               align = "left",
                               style = list(fontFamily = "monospace", whiteSpace = "pre"))
          ))
r
```

and save as html
```{r}
html_file <- "table.html"
saveWidget(widget = r, file = html_file, selfcontained = TRUE)
```

# get data round 2: srf accounts
```{r}
handles_srf <- c("SRF", "SRFnews", "SRFdata", "srfmeteo", "SRGSSR", "srfkonsum")
user_characteristics_srf <- tibble(handles_srf) %>%
  rename(handles = handles_srf) %>%
  mutate(data_user = purrr::map(.x=handles, .f=get_characteristics, headers=headers)) %>%
  tidyr::unnest(cols = c(data_user))
tweets_srf <- tibble(handles_srf) %>%
  rename(handles = handles_srf) %>%
  mutate(data_recent_tweets = purrr::map(.x=handles, .f=get_recent_tweets, headers=headers)) %>%
  tidyr::unnest(cols = c(data_recent_tweets)) %>%
  mutate(likes = purrr::map(.x=data.id, .f=get_n_likes, headers = headers))
```

```{r}
# rename columns
user_characteristics_srf <- clean_column_names(user_characteristics_srf) 

# summarise tweets
tweet_summary_srf <- summarise_tweets(tweets_srf)
```


select a subset of the user characteristics and join with the tweet summary
```{r}
subset_srf <- user_characteristics_srf %>%
  select(name = handles, since, followers = followers_count, tweets = tweet_count) %>%
  full_join(tweet_summary_srf, by = c(name = "handles"))
```

download all the profile pictures
```{r}
download_profile_pics(user_characteristics_srf)
```

duplicate name column for image
```{r}
subset_srf <- subset_srf %>%
  mutate(image_twitter = name) %>%
  relocate(image_twitter, .before = name)
```

```{r}
my_font <- "corbel"
r_srf <- reactable(subset_srf,
          defaultSorted = "since", defaultSortOrder = "desc",
          columns = list(
            image_twitter = colDef(name = "", 
                          width = 60,
                          cell = function(value) {
                               img_src <- knitr::image_uri(sprintf("images/%s.jpg", value)) # .png for the manual download, .jpg for automatic
                               image <- img(src = img_src, height = "28px", alt = "")
                               tagList(
                                 div(style = list(display = "inline-block", width = "45px"), image),
                                 )
                               }),
            name = colDef(name = "Twitter-Konto", 
                          format = colFormat(prefix = "@"),
                          width = 150,
                          style = list(fontFamily = my_font)),
            since = colDef(name = "dabei seit",
                           align = "center",
                           style = list(fontFamily = my_font)),
            followers = colDef(name = "Follower",
                               cell = function(value){
                                 width <- paste0(value*100 / max(subset$followers), "%")
                                 value <- format(value, width = 7, justify = "right")
                                 bar_chart(value, width=width, fill = "#AF001D", background = "#e1e1e1")
                               },
                               align = "left",
                               width = 180,
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            tweets = colDef(name = "Tweets total",
                            cell = function(value){
                                 width <- paste0(value*100 / max(subset$tweets), "%")
                                 value <- format(value, width = 9, justify = "right")
                                 bar_chart(value, width=width, fill = "#0D446F", background = "#e1e1e1")
                               },
                               align = "left",
                              width = 180,
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            recent_tweets = colDef(name = "Tweets letzte Woche",
                                   cell = function(value){
                                 width <- paste0(value*100 / max(subset$recent_tweets), "%")
                                 value <- format(value, width = 5, justify = "right")
                                 bar_chart(value, width=width, fill = "#12588E", background = "#e1e1e1")
                               },
                               align = "left",
                               style = list(fontFamily = "monospace", whiteSpace = "pre")),
            recent_likes = colDef(name = "Likes letzte Woche",
                                  cell = function(value){
                                 width <- paste0(value*100 / max(subset$recent_likes), "%")
                                 value <- format(value, width = 5, justify = "right")
                                 bar_chart(value, width=width, fill = "#1A7AC5", background = "#e1e1e1") #5B5A54
                               },
                               align = "left",
                               style = list(fontFamily = "monospace", whiteSpace = "pre"))
          ))
r_srf
```


and save as html
```{r}
html_file_srf <- "table_srf.html"

saveWidget(widget = r_srf, file = html_file_srf, selfcontained = TRUE)
```
